The Blue Obelisk five years on

### 2011-03-02 paper.tex
Something about applications building on toolkits

>>>>

...something about toolkits...

Although feature-rich and robust cheminformatics toolkits are useful in and of themselves, they can also be seen as providing a base layer on which tools and applications can be built. Now that these toolkits have reached an acceptable level of stability and functionality, an increasing amount of software is being developed using these toolkits. As an example of the interaction between the commercial and open source worlds, Silicos (a Belgian company that provides services in the area of cheminformatics XXXX rephrase), has released several command line applications based on Open Babel; Pharao for pharmacophore generation (Sept 2010?), Sieve for filtering by molecular property, .....

It is worth noting that Pharao is the first Open Source pharmacophore program (\emph{Is this a reasonable statement?) (although pharmacophore-related functionality has been available in the CDK and RDKit for some time).

The availability of feature-rich and robust cheminformatics toolkits has started to bear fruit in the development of higher-level tools and applications that are built using these toolkits.
